Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-10-31 doc/prelim/presentation/prelim_presentation.tex
working on research plan

%%---------------------------------------------------------------------------%%
\begin{frame}{Projection Method Notes}

\begin{itemize}
  \item Global reduction operations observed not to impede scalability
    \begin{itemize}
    \item Dot product
    \item Vector norms
    \end{itemize}
  \item Nearest neighbor computations have poor algorithmic strong
    scaling
    \begin{itemize}
      \item Matrix-vector multiply
      \item Weak scaling is better
    \end{itemize}

\end{itemize}

@@

@@

@@

>>>>

%%---------------------------------------------------------------------------%%
\begin{frame}{Projection Methods Summary}

  \begin{itemize}
  \item Used in practice everywhere
  \item Global reduction operations observed not to impede scalability
    \begin{itemize}
    \item Dot product
    \item Vector norms
    \end{itemize}
  \item Nearest neighbor computations have poor algorithmic strong
    scaling
    \begin{itemize}
    \item Matrix-vector multiply
    \item Weak scaling is better
    \end{itemize}
  \end{itemize}

@@

  \begin{itemize}
  \item Need a framework to generate linear and nonlinear systems in
    parallel
    \begin{itemize}
    \item Linear algebra data structures
    \item Parallel communication framework
    \item Mesh generation and partitioning
    \item Automatic differentiation and more...
    \end{itemize}
  \item Choose the finite element method to leverage a finite element
    assembly engine
  \end{itemize}

  \[
  \ve{A}(\ve{u}) = \ve{0},\ \forall \ve{u} \in \Omega
  \]
  \[
  \ve{B}(\ve{u}) = \ve{0},\ \forall \ve{u} \in \Gamma
  \]
  \[
  \int_{\Omega} \ve{v}^T \ve{A}(\ve{u}) d\Omega + \int_{\Gamma}
  \bar{\ve{v}}^T \ve{B}(\ve{u}) d\Gamma = \ve{0}
  \]
  \[
  \int_{\Omega} \ve{C}(\ve{v}^T) \ve{D}(\ve{u}) d\Omega +
  \int_{\Gamma} \ve{E}(\bar{\ve{v}}^T) \ve{F}(\ve{u}) d\Gamma = \ve{0}
  \]

@@

  \begin{itemize}
  \item Analytic solution to the heat equation for the linear methods
  \item Sequence of Navier-Stokes benchmarks for the nonlinear methods
    \begin{itemize}
    \item Thermal convection cavity problem (De Vahl Davis, 1983)
    \item Lid driven cavity problem (Ghia et al., 1982)
    \item Backward-Facing step problem (Gartling, 1990)
    \end{itemize}
  \item Tuning benchmark parameters varies the strength of
    nonlinearities
  \end{itemize}

  \begin{columns}
    \begin{column}{0.5\textwidth}
      \[
      \rho \ve{u} \cdot \nabla \ve{u} - \nabla \cdot \ve{T} - \rho
      \ve{g} = \ve{0}
      \]
      \[
      \nabla \cdot \ve{u} = 0
      \]
      \[
      \rho C_p \ve{u} \cdot \nabla T + \nabla \cdot \ve{q} = 0
      \]
    \end{column}

    \begin{column}{0.5\textwidth}
      \[
      \ve{T} = -P \ve{I} + \mu[\nabla \ve{u} + \nabla \ve{u}^T]
      \]
      \[
      \ve{q} = - k \nabla T
      \]
    \end{column}
  \end{columns}

@@

  Domain Overlap Studies for the Parallel Neumann-Ulam Method

  Domain Replication Studies for the Parallel Neumann-Ulam Method

  Parallel Performance and Numerical Accuracy Studies for the MCSA
  Method

  Parallel Performance and Numerical Accuracy Studies for the FANM
  Method
